### 2020-05-28 case-studies.tex
added note about cursor inspector
tweaked note about cursor inspector
added section on parameters and partial application

\subsubsection{Livelit Expansion} abc

\subsubsection{Typed Hygienic Splicing} abc

@@

>>>>

\subsubsection{Livelit Expansion} 
Livelit expressions are given dynamic meaning by expansion to core expressions, i.e. expressions that do not contain livelits.
For example, the expansion of Fig.~\ref{fig:grading} is:\todo{change code once figure is final}{}

\begin{lstlisting}
let grades = Dataframe (
  ["A1", "A2", "A3", "A4", "Midterm", "Final"],
  [
    ("Cyrus", [0.0, 0.0, 0.0, 0.0, 0.0]),
    ("Nick", [0.0, 0.0, 0.0, 0.0, 0.0]),
    ("David", [0.0, 0.0, 0.0, 0.0, 0.0])
  ]) in 
let averages = compute_averages(grades) in 
let cutoffs = (.A 90.0, .B 80.0, .C 70.0, .D 60.0) in 
format_for_university(assign_grades(averages, cutoffs))
\end{lstlisting}

The programmer can inspect this expansion in Hazel. 
Ideally, however, it would not be necessary to inspect the expansion 
(or the livelit implementation, which specifies the expansion logic and is discussed in Sec.~\ref{sec:livelit-definitions}) 
to reason about types and binding. 
After all, one does not need to look inside 
function bodies to reason about types and binding.
Instead, in the words of Reynolds\todo{cite}{}, 
``type structure is a syntactic discipline for maintaining levels of abstraction''.
The livelits mechanism supports reasoning abstractly about types and binding by 
several means.

To support abstract reasoning about the type of the expansion, 
livelit definitions declare an \emph{expansion type}.
The declarations of the two livelits in Fig.~\ref{fig:grading}, 
eliding their implementations, are:
\begin{lstlisting}[numbers=none]
livelit $dataframe at Dataframe { ... }
livelit $cutoffs(avgs: List(Float)) 
  at (.A Float, .B Float, .C Float, .D Float) { ... }
\end{lstlisting}
The expansion type of \li{\$dataframe} is \li{Dataframe} 
(a type classifying tabular floating point data together with string row and column keys, consistent with the expansion above)
and the expansion type of \li{\$cutoffs} is a labeled product of grade cutoffs (Hazel notates labels \li{.label}).
Hazel summarizes the typing information from the livelit definition for the programmer when the cursor is on the livelit's name, 
just as it displays a function's type when its name is under the cursor (not shown).\todo{could show if Hannah et al are finished}{}

\subsubsection{Typed Hygienic Splicing and Parameterization} 
Livelit expressions can have sub-expressions provided by the client in one of two ways:
as parameters or as splices.

\paragraph{Parameters} Parameters appear immediately after the livelit name. 
For example, \li{averages} is provided as a parameter to \li{\$cutoffs} in Fig.~\ref{fig:grading}.
Livelits can declare a fixed number of parameters and specify their types in their declarations. 
For example, the declaration of \li{\$cutoffs} above specifies one parameter of type \li{List(Float)}.
Parameters can be partially applied in livelit abbreviations. For example, consider the slider livelit
from Fig.~\ref{fig:color}:
\begin{lstlisting}[numbers=none]
livelit $slider (min: Float) (max: Float) at Float { ... }
\end{lstlisting}
We can partially apply the first parameter as follows to create a non-negative slider with one remaining parameter:
\begin{lstlisting}[numbers=none]
livelit $nnslider = $slider 0.0 in ...
\end{lstlisting}
The client must provide all remaining parameters to use a livelit to fill a hole in the program.
So writing \li{\$nnslider} in expression position will not display the slider GUI. Instead, it will display as a livelit parameterization error.%
\footnote{In Hazel, erroneous expressions are placed inside holes so that they do not prevent other parts of the program from executing
\cite{HazelnutLive}.}

We can apply both parameters in an abbreviation to create an unparameterized livelit:
\begin{lstlisting}[numbers=none]
livelit $percentage = $slider 0.0 1.0 in ...
\end{lstlisting}

\paragraph{Splices} Splices appear directly inside the livelit GUI.
For example, the column headings and the cells in the \li{\$}

unlike arguments, not a fixed number of splices (e.g. adding a new row or column by pressing those buttons)

@@

Ideas:
\begin{itemize}
  \item derivation trees like Joomy's system (\url{https://joom.github.io/proof-tree-builder/src/})
\end{itemize}
